---
title: "ggmagnolia"
output: github_document
---

```{r echo=FALSE}
knitr::opts_chunk$set( fig.path = "man/figures/")
```
<!-- badges: start -->
[![Lifecycle:maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![DOI](https://joss.theoj.org/papers/10.21105/joss.02472/status.svg)](https://doi.org/10.21105/joss.02472)
<!-- badges: end -->

## Citation
[to come]

Please have a look also to 

- [tidyHeatmap](https://github.com/stemangiola/tidyHeatmap/) for tidy high-level data analysis and manipulation 
- [tidygate](https://github.com/stemangiola/tidygate/) for adding custom gate information to your tibble 
- [tidySingleCellExperiment](https://stemangiola.github.io/tidySingleCellExperiment/) for tidy manipulation of Seurat objects
- [tidyseurat](https://stemangiola.github.io/tidyseurat/) for tidy manipulation of Seurat objects
- [tidybulk](https://stemangiola.github.io/tidybulk/) for tidy high-level data analysis and manipulation 
- [tidySummarizedExperiment](https://stemangiola.github.io/tidySummarizedExperiment/) for heatmaps produced with tidy principles

website: [stemangiola.github.io/ggmagnolia](https://stemangiola.github.io/ggmagnolia/)

`ggmagnolia` is a package that introduces tidy principles to the creation of information-rich heatmaps. 
This package uses [ComplexHeatmap](https://bioconductor.org/packages/release/bioc/html/ComplexHeatmap.html) as graphical engine.


## Functions/utilities available

Function | Description
------------ | -------------
`heatmap` | Plot base heatmap
`add_tile` | Add tile annotation to the heatmap


## Installation

To install the most up-to-date version

```{r, eval=FALSE}

devtools::install_github("stemangiola/ggmagnolia")


```


To install the most stable version (however please keep in mind that this package is under a maturing lifecycle stage)

```{r, eval=FALSE}

install.packages("ggmagnolia")

```

## Contribution

If you want to contribute to the software, report issues or problems with the software or seek support please open an issue [here](https://github.com/stemangiola/ggmagnolia/issues)

## Input data frame

The heatmaps visualise a multi-element, multi-feature dataset, annotated with independent variables. Each observation is a element-feature pair (e.g., person-physical characteristics).

element | feature | value | independent_variables
------------ | ------------- | ------------- | -------------
`chr` or `fctr` | `chr` or `fctr` | `numeric` | ...

Let's transform the mtcars dataset into a tidy "element-feature-independent variables" data frame. Where the independent variables in this case are 'hp' and 'vs'.

```{r, echo=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggmagnolia)
data("magnolia_input")
```

```{r}
 magnolia_input |> 
		plot_polar()
```

